timesliced_random_cell_selection

### 2018-10-30 src/timesliced_random_cell_selection.Rmd
added depth to the timesliced cell randomisation process

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
Th
```{r pre-install packages, message=FALSE}
packages <- c("raster")
source("../src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

ok so now I have a base list to work off...

Split the data_aea into timeslices (year/month).
All you need is the year, month, cell_id
```{r}
cell_yymm <- subset(data_aea, select= c(cell_id, year, month)) #create a new df with just cell_id, yr, month
split_cell_yymm <- split(cell_yymm, list(cell_yymm$year, cell_yymm$month), drop = TRUE)
```

What I want to do is for each time slice, create a list of all cells, then remove the ones where observations occured
ly name the output (and create a .csv with the name of the level being worked on)

@@

```{r}
no_timeslices <- length(split_cell_yymm) # how many levels (time slices) are in the list
for (i in 1:no_timeslices){
  timeslice <- split_cell_yymm[[i]]
  timeslice <- as.data.frame(test_timeslice)
  time_cell <- unique_cell_centroid
  time_cell <- test_time_cell[!test_time_cell$cell_id %in% test_timeslice$cell_id, , drop = FALSE]
  write.csv(test_time_cell, paste0(names(lapply(split_cell_yymm, names))[i], ".csv"), row.names = FALSE) 
}
```

Ok so now I have a bunch of .csv files containing cells where no observations occurred for a given timeslice.
Next step is to randomly select cells in each timeslice. Make sure you generate new files for each...

@@

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
Th
```{r pre-install packages, message=FALSE}
packages <- c("raster", "dplyr")
source("../src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

ok so now I have a base list to work off... This gives you a dataset of xy points, but you need xyz (where z is based on the depth layers in the environmental data)
```{r}
unique_cell_xyz <- unique_cell_centroid
unique_cell_xyz$depthlayerno <- NA
unique_cell_xyz <- unique_cell_xyz[rep(seq_len(nrow(unique_cell_xyz)), each=50),] #this generates 50 repetitions of each row
unique_cell_xyz$depthlayerno <- rep(1:50) #assign 1:50 on a repeating cycle to the depth column. 50 is chosen because there are 50 depth layers
unique_cell_xyz$id_depth <- paste(unique_cell_xyz$cell_id, unique_cell_xyz$depthlayerno, sep="") #create a new column that is a unique cell_id & depth ID. This is to help remove cells later and randomise
```

Split the data_aea into timeslices (year/month).
All you need is the year, month, cell_id, and depthlayerno
```{r}
cell_yymm <- subset(data_aea, select= c(cell_id, depthlayerno, year, month)) #create a new df with just cell_id, yr, month
cell_yymm$id_depth <- paste(cell_yymm$cell_id, cell_yymm$depthlayerno, sep="") #create a new column that is a unique cell_id & depth ID. This is to help remove cells later and randomise
split_cell_yymm <- split(cell_yymm, list(cell_yymm$year, cell_yymm$month), drop = TRUE)
```

What I want to do is for each time slice, create a list of all cells (xyz), then remove the ones where observations occuredand create a .csv with the name of the level being worked on

@@

```{r}
no_timeslices <- length(split_cell_yymm) # how many levels (time slices) are in the list
for (i in 1:no_timeslices){
  timeslice <- split_cell_yymm[[i]]
  timeslice <- as.data.frame(timeslice)
  time_cell <- unique_cell_xyz
  time_cell <- time_cell[!time_cell$id_depth %in% timeslice$id_depth, , drop = FALSE]
  write.csv(time_cell, paste0(names(lapply(split_cell_yymm, names))[i], ".csv"), row.names = FALSE) 
}
```

Ok so now I have a bunch of .csv files containing cells where no observations occurred for a given timeslice on xyz coordinates.
Next step is to randomly select cells in each timeslice. Make sure you generate new files for each...

@@

manual attempt:
```{r}
library(dplyr)
test_cell_selection <- read.csv("../output/bio/background/1998.10.csv", header = TRUE) #just load one csv to play with
test_ran_cell_sel <- sample_n(test_cell_selection, 10) #where 10 = number of rows to sample
```
